---
title: "mcxs-a2-g5 report"
author: "Alex Rendell, Xinyu Dang, Gavin Williams"
date: "29/04/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exercise 1 - 

In this section, we will (i) List and justify the selection of nine macroeconomic variables used to forecast 'Hours Worked', (ii) Source and transform the data for the ten variables into a data matrix, and (iii) Plot the data matrix and comment with observations
````{r}

`````

# Exercise 2
In this section we document the likelihood function of the model, and the probability density function of A and \Sigma which follows joint matrix-variate normal-inverse Wishart distribution, and includes two hyperparameters.
\newpage

**Exercise 2.**

![] (Exercise 2.png)




We also specify the parameters determining the prior distribution matrices \bar{A}, \bar{V}, \bar{S} and \bar{v}.



# Exercise 3 - Joint conditional posterior distribuion





# Exercise 4






# Exercise 5




# Exercise 6




# Exercise 7






# Exercise 8



# Exercise 9 